\documentclass[10pt,conference,letterpaper]{IEEEtran}
%\usepackage{amsmath,epsfig,multirow,color,latexsym}
\usepackage{graphicx}
\usepackage{subfigure}
\newtheorem{defi}{Definition}  % 在 preamble 區先定義好環境名稱
\usepackage{listings}
\usepackage{amssymb}
\usepackage{comment}
\usepackage[ruled,linesnumbered,noend]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize{#1}}
\SetCommentSty{mycommfont}
\usepackage{textcomp}
\usepackage{multirow}


\graphicspath{{figure/}}

\begin{document}
\title{KSTR: Keyword-aware Skyline Travel Route Recommendation}

\author{
\IEEEauthorblockN{Yu-Ting Wen\IEEEauthorrefmark{1},
Kae-Jer Cho\IEEEauthorrefmark{1},
Wen-Chih Peng\IEEEauthorrefmark{1},
Jinyoung Yeo\IEEEauthorrefmark{2},
Seung-won Hwang\IEEEauthorrefmark{3}
}
\IEEEauthorblockA{\IEEEauthorrefmark{1}National Chiao Tung University, Taiwan}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pohang University of Science and Technology, Republic of Korea}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Yonsei University, Republic of Korea}
{\{ytwen,kjcho13,wcpeng\}@cs.nctu.edu.tw,jinyeo@postech.ac.kr,seungwonh@yonsei.ac.kr}
}

\maketitle

\begin{abstract}
With the popularity of social media (e.g., Facebook and Flicker), users could easily share their check-in records and photos during their trips. In view of the huge amount of check-in data and photos in social media, we intend to discover travel experiences to facilitate trip planning. Prior works have been elaborated on mining and ranking existing travel routes from check-in data. We observe that when planning a trip, users may have some keywords about preference on his/her trips. Moreover, a diverse set of travel routes is needed. To provide a diverse set of travel routes, we claim that more features of Places of Interests (POIs) should be extracted. Therefore, in this paper, we propose a Keyword-aware Skyline Travel Route (\textit{KSTR}) framework that use knowledge extraction from historical mobility records and the user's social interactions. Explicitly, we model the ``Where, When, Who'' issues by featurizing the geographical mobility pattern, temporal influence and social influence. Then we propose a keyword extraction module to classify the POI-related tags automatically into different types, for effective matching with query keywords. We further design a route reconstruction algorithm to construct route candidates that fulfill the query inputs. To provide diverse query results, we explore Skyline concepts to rank routes. To evaluate the effectiveness and efficiency of the proposed algorithms, we have conducted extensive experiments on real location-based social network datasets, and the experimental results show that \textit{KSTR} does indeed demonstrate good performance compared to state-of-the-art works. 
\end{abstract}

\input{1_introduction-v1}
\input{2_framework_v1}
\input{3_2_feature-v1}
\input{4_skyline_v1}
\input{5_experiment-v1}

\nocite{PGT2014,Ye2012,WSDM2012finding,VLDB2010,ICDE2013,SDM2011,SIGMOD2010,rendle2010factorizing,WWW2009,ye2011exploiting,photo2trip,BBS,yuan2014graph,ge2010energy,MM2010,cao2012keyword,zheng2015approximate,SIGKDD07_TPM}

\section{Conclusion}
\vspace{-1mm}
In this paper, we study the travel route recommendation problem. We have developed a \textit{KSTR} framework to suggest travel trajectories with a specific range and a set of user preference keywords. These travel trajectories are related to all or partial user preference keywords, and are recommended based on (i) the attractiveness of the POIs it passed, (ii) visiting the POIs at their corresponding proper arrival time, and (iii) the route generated by influential users. We propose a novel keyword extraction module to identify the semantic meaning and match measurement of routes, and design a route reconstruction algorithm to aggregate trajectory segments into travel routes in accordance with query range and time period. We leverage score functions for the three aforementioned features and adapt Skyline search for travel route recommendation instead of the traditional top-$K$ system. The experimental results demonstrate that \textit{KSTR} is able to retrieve travel routes that are interesting for users and outperforms baseline algorithms in terms of effectiveness and efficiency.
\vspace{-1mm}
% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}
Wen and Peng were supported in part by MOST Taiwan, Project No. 102-2221-E-009 -171 -MY3  and 104-2221-E-009 -138 -MY2, by Academic Sinica Theme project, Project No. AS-102-TPA06. Hwang and Yeo were supported by ICT R\&D program of MSIP/IITP [B0101-15-0307] and Microsoft Research.

\vspace{-1mm}

\IEEEpeerreviewmaketitle
\scriptsize
\bibliographystyle{IEEEtran}
\bibliography{reference}

% that's all folks
\end{document}


